Title

### 2025-02-07 index.qmd
adding rq2 for houston

# 3) Subset of metros with RQ2 data (2 orders each)
rq2_metros <- c(
  "chicago", "philadelphia", "los angeles", 
  "orange county", "san diego", "bay area",
  "northern new jersey","long island",'detroit','dallas'
)

# We'll define a "metro_orders" list for those RQ2 metros:
metro_orders <- list(
  "chicago"             = c("487984", "488035_488053"),
  "philadelphia"        = c("448922", "448427_448440"),
  "northern_new_jersey" = c("448922", "448427_448440"),
  "long_island"         = c("448922", "448427_448440"),
  "detroit"             = c("448922", "448427_448440"),
  "dallas"              = c("448922", "448427_448440"),
  "los_angeles"         = c("448375", "448374_448420"),
  "orange_county"       = c("448375", "448374_448420"),
  "san_diego"           = c("448375", "448374_448420"),
  "bay_area"            = c("448375", "448374_448420")
)

>>>>

# 3) Subset of metros with RQ2 data (2 orders each)
rq2_metros <- c(
  "chicago", "philadelphia", "los angeles", 
  "orange county", "san diego", "bay area",
  "northern new jersey","long island",'detroit','dallas','houston'
)

# We'll define a "metro_orders" list for those RQ2 metros:
metro_orders <- list(
  "chicago"             = c("487984", "488035_488053"),
  "philadelphia"        = c("448922", "448427_448440"),
  "northern_new_jersey" = c("448922", "448427_448440"),
  "long_island"         = c("448922", "448427_448440"),
  "detroit"             = c("448922", "448427_448440"),
  "dallas"              = c("448922", "448427_448440"),
  "los_angeles"         = c("448375", "448374_448420"),
  "orange_county"       = c("448375", "448374_448420"),
  "san_diego"           = c("448375", "448374_448420"),
  "bay_area"            = c("448375", "448374_448420"),
  'houston'             = c('329702') #   # houston = c('houston', 'houston_eps_codes', 'PSAT score 1010 - 1520', '329702')

)
